---
title: "Ardalan Mirshani's CV"
author: Ardalan Mirshani
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
# knitr::opts_chunk$set(
#   results='asis', 
#   echo = FALSE
# )
# 
# library(magrittr) # For the pipe
# library(fontawesome)
# source("cv_printing_functions.r")
# 
# # Read in all data and initialize a CV printer object
# CV <- create_CV_object(
#   data_location = "https://docs.google.com/spreadsheets/d/1m14pQsl6kJ4ZcCpgkPPfnhNRjWgQpi3kWjtZ03-mBxc/edit#gid=917338460",  
#   pdf_mode = params$pdf_mode
# )

```

```{r, include=FALSE}
## When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
# if(params$pdf_mode) {
#     cat("
# <style>
# :root{
#   --decorator-outer-offset-left: -6.5px;
# }
# </style>")
# }
```

# Aside

```{r, include=FALSE}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
#atadrivencv::build_network_logo(CV$entries_data)
```

```{r, include=FALSE}
# if(params$pdf_mode){
#   cat("View this CV online with links at _nickstrayer.me/cv/_")
# } else {
#   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf)")
# }
```

## Contact Info {#contact}

-   <i class='fa fa-envelope'></i> [ardeeshany\@gmail.com](mailto:ardeeshany@gmail.com)
-   <i class='fa fa-home'></i> [mirshani.com](https://mirshani.com)
-   <i class='fa fa-twitter'></i> [ArdalanMirshani](https://twitter.com/ArdalanMirshani)
-   <i class='fa fa-github'></i> [ardeeshany](https://www.github.com/ardeeshany)
-   <i class='fa fa-linkedin'></i> [mirshani](https://www.linkedin.com/in/mirshani)

## <i class="fab fa-r-project fa-lg"></i> Programming {#skills}

- <i class="fa fa-laptop fa-lg"></i> 
<span style="font-weight:bold"> Web development:</span> <br>
Expert in {Shiny} + HTML/CSS/JS, {blogdown}

- <i class="fa fa-robot fa-lg"></i> 
<span style="font-weight:bold"> Automation Environment:</span> 
R-pkg dev, Workflow pkgs {usethis, golem, targets}, {renv}, {testthat}, {profvis}, chatty functions

- <i class="fa fa-book fa-lg"></i> 
<span style="font-weight:bold"> Reproducible Reporting:</span> {rmarkdown}, {bookdown}, {pagedown},  Latex

- <i class="fa fa-chart-bar fa-lg"></i> 
<span style="font-weight:bold"> Interactive Visualizations:</span> 
ggplot2, htmlwidgets pkgs {DT, Plotly, Leaflet, etc.}, {gt}

- <i class="fa fa-search fa-lg"></i> 
<span style="font-weight:bold"> Data Exploration and Wrangling:</span> 
Fan of {tidyverse}, Efficient coding advocate.

- <i class="fa fa-cube fa-lg"></i> 
<span style="font-weight:bold"> Modeling and Machine Learning:</span>
{Tidymodels} Framework

- <i class="fa fa-code-branch fa-lg"></i> 
<span style="font-weight:bold"> Workflow:</span>
git, GitHub, Travis/Runner, agile

<!-- ::: {.skill-bar style="background:linear-gradient(to right, -->
<!--                                       #969696 100%, -->
<!--                                       #d9d9d9 100% 100%)"} -->
<!-- R2 -->
<!-- ::: -->

# Main

## Ardalan Mirshani {#title}

[I am a **Data Scientist** and **Statistical web app developer** with an <br> interest on creating scientific tools, reproducible workflows, and automating repetitive tasks that arise during all data wrangling, exploring, visualizing, modeling, and reporting processes.]{style="font-size:14px; text-align: justify;
  text-justify: inter-word;"}

## Professional Experience {data-icon="suitcase"}

### Sr Expert Data Science

Novartis

Cambridge, MA

Present - 10-2019

- [Creating generalizable and reusable statistical tools, advance interactive visualizations, automation workflows, high performance computing, <br> scientific reproducible templates and reports for analytics activities.]{style='text-align: justify;
  text-justify: inter-word;'}
- Developing production-grade shiny apps, modules, and R-packages to support exploratory machine learning projects.
- Designing educational training materials and consulting for internal quantitative scientists.

### Shiny app developer (Internship)

Novartis ([Recommendation](https://www.linkedin.com/in/mirshani/))

Cambridge, MA

08-2018 - 05-2018

- Implementing modularized R Shiny apps for analyzing clinical trials.

### Statistical Consultant

PSU Statistical Consulting Center

University Park, PA

2016

- Applications of statistical methods in the consulting environment.

## Education {data-icon="graduation-cap" data-concise="true"}

### PhD, Statistics

Pennsylvania State University

University Park, PA

2019 - 2014

- Thesis: [Regularization Methods in Functional Data Analysis](https://etda.libraries.psu.edu/catalog/16828azm245)

### M.Sc, Mathematics

Sharif University of Technology

Iran

2013 - 2011

### B.Sc, Electrical Engineering

KNTU

Iran

2011 - 2006

## Freelance Experience {data-icon="laptop"}

### [Brand Loyalty Lab](https://brandloyaltylab.com)

A series of research and development on retail market brand loyalty.

N/A

Now - 2019

### [RAAVI](https://ardeeshany.shinyapps.io/Raavi_en/)

A complicated modularized Shiny app for analyzing students' scores.

N/A

2018 - 2017

::: {.aside}
[Other Languages:]{style="font-family: 'Montserrat', sans-serif; font-size:18px;"}

- <i class="fab fa-python fa-lg"></i> 
<span style="font-weight:bold"> Python:</span> 
My second <br> language, {reticulate}

- <i class="fa fa-code fa-lg"></i> 
<span style="font-weight:bold"> Julia:</span> Exploration

- <i class="fa fa-terminal fa-lg"></i> 
<span style="font-weight:bold"> Script:</span> Bash
:::

<!-- These breaks just force a new page so section doesnt get cut off -->

## Certificates {data-icon="certificate"}

### Data Science

DataCamp ([Certificates](https://www.linkedin.com/in/mirshani/))

N/A

2020 - 2018

- Exploring +40 `Datacamp` courses on the state of the art pkgs in Data wrangling, visualizing, modeling, reporting, Big data, databases, and more for thinking and coding more efficient.

::: {.aside}
<br> <br> <br> <br> <br> <br> <br> <br>
[Cheatsheet]{style="font-family: 'Montserrat', sans-serif; font-size:18px;"}

- <i class="fa fa-align-justify fa-lg"></i> <span style="font-weight:bold"> [Parallel Computing](https://github.com/rstudio/cheatsheets/raw/master/parallel_computation.pdf):</span> <br> Contributed to RStudio Cheatsheet
:::

## Research Experience {data-icon="newspaper"}

### [Adaptive function-on-scalar regression with a smoothing elastic net]{style='font-size:12.2px;'}

Submitted to JMVA ([Article](https://arxiv.org/abs/1905.09881))

N/A

2020 - 2018

- [{AFSSEN} R-Package](https://github.com/ardeeshany/AFSSEN): A very fast coordinate descent algorithm (`C++` backend) for running function-on-scalar regression in high-dim data.

### Formal privacy for functional data with gaussian perturbations

ICML 2019 ([Article](http://proceedings.mlr.press/v97/mirshani19a.html))

N/A

2019 

- Developed a [Shiny app](https://ardeeshany.shinyapps.io/private_face/) for exploring privacy in 3D facial data.

::: {.aside}
[Everyday Learning:]{style="font-family: 'Montserrat', sans-serif; font-size:18px;"}

- <i class="fab fa-twitter fa-lg"></i> 
<span style="font-weight:bold"> R Community:</span> <br>
Following `#TidyTuesday`, `#Rstats`, `#dataviz`, `#RLadies`,  Screencasts

:::

## Teaching Experience {data-icon="chalkboard-teacher"}

### Lecturer: Probability, statistics and Calculus

Tehran Virtual University

Iran

2008

## Awards {data-icon="trophy"}

### CD&A Best Poster Presentation Awards

A Shiny app for exploring safety and efficacy of Heme data

Novartis

2020

### Rao Prize Best Poster Presentation Awards

Privacy in functional data analysis

PSU

2017

### Silver Medal

35th Iranian National Mathematics Competition for university

Iran

2011

## Disclaimer {#disclaimer}

Made with [pagedown](https://github.com/rstudio/pagedown) 

Source code from [nstrayer](https://github.com/nstrayer/cv)

Last updated on `r Sys.Date()`.
